ECCCos from the Black Box:\\ Faithful Explanations through\\ Energy-Constrained Conformal Counterfactuals

### 2023-12-12 paper/tables.Rmd
choices made for tables

```{r}
# Choices:
measures <- c(
  "unfaithfulness",
  "implausibility",
  "set_size_penalty"
)
measure_names <- c(
  "Unfaithfulness ↓",
  "Implausibility ↓",
  "Uncertainty ↓"
)
chosen_source <- "tabular"
# Order:
chosen_data <- c(
  "California Housing",
  "GMSC"
)
chosen_model <- c(
  "MLP",
  "JEM Ensemble"
)

@@

# Logic:
tab_i <- tab_i[variable %in% measures]
tab_i[,variable:=factor(variable, levels=measures)]
tab_i <- tab_i[dataname %in% chosen_data]
tab_i <- tab_i[model %in% chosen_model]
tab_i[,model:=factor(model,levels=chosen_model)]
tab_i[,dataname:=factor(dataname,levels=chosen_data)]
tab_i <- dcast(tab_i, model + generator ~ dataname + variable)
col_names <- c(
  "Model",
  "Generator",
  rep(measure_names,length(chosen_data))
)
caption <- sprintf(
  "Results for %s datasets: sample averages +/- one standard deviation across counterfactuals. Best outcomes are highlighted in bold. Asterisks indicate that the given value is more than one (*) or two (**) standard deviations away from the baseline (\\textit{Wachter}). \\label{tab:results-%s} \\newline",
  chosen_source,
  chosen_source
)
file_name <- sprintf(
  "paper/contents/table-%s.tex",
  chosen_source
)
sub_header <- rep(length(measures), length(chosen_data))
names(sub_header) <- chosen_data
header <- c(
  " " = 2, sub_header
)
line_sep <- c(rep("",length(measures)-1),"\\addlinespace")
algin_cols <- c(rep('l',2),rep('c',ncol(tab_i)-2))
kbl(
  tab_i, caption = caption, 
  align = algin_cols, col.names=col_names, booktabs = T, escape=F, 
  format="latex", linesep = line_sep, table.env="table*"
) %>%
  kable_styling(
    latex_options = c("scale_down")
  ) %>%
  kable_paper(full_width = F) %>%
  add_header_above(header) %>%
  collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
  save_kable(file_name)
```

>>>>

```{r}
# Choices:
measures <- c(
  "unfaithfulness",
  "implausibility",
  "set_size_penalty"
)
measure_names <- c(
  "Unfaithfulness ↓",
  "Implausibility ↓",
  "Uncertainty ↓"
)
chosen_source <- "tabular"
# Order:
chosen_data <- c(
  "California Housing",
  "GMSC"
)
chosen_model <- c(
  "MLP Ensemble",
  "JEM Ensemble"
)

@@

# Logic:
tab_i <- tab_i[variable %in% measures]
tab_i[,variable:=factor(variable, levels=measures)]
tab_i <- tab_i[dataname %in% chosen_data]
tab_i <- tab_i[model %in% chosen_model]
tab_i[,model:=factor(model,levels=chosen_model)]
tab_i[,dataname:=factor(dataname,levels=chosen_data)]
tab_i <- dcast(tab_i, model + generator ~ dataname + variable)
col_names <- c(
  "Model",
  "Generator",
  rep(measure_names,length(chosen_data))
)
caption <- sprintf(
  "Results for %s datasets: sample averages +/- one standard deviation across valid counterfactuals. Best outcomes are highlighted in bold. Asterisks indicate that the given value is more than one (*) or two (**) standard deviations away from the baseline (\\textit{Wachter}). \\label{tab:results-%s} \\newline",
  chosen_source,
  chosen_source
)
file_name <- sprintf(
  "paper/contents/table-%s.tex",
  chosen_source
)
sub_header <- rep(length(measures), length(chosen_data))
names(sub_header) <- chosen_data
header <- c(
  " " = 2, sub_header
)
line_sep <- c(rep("",length(measures)-1),"\\addlinespace")
algin_cols <- c(rep('l',2),rep('c',ncol(tab_i)-2))
kbl(
  tab_i, caption = caption, 
  align = algin_cols, col.names=col_names, booktabs = T, escape=F, 
  format="latex", linesep = line_sep, table.env="table*"
) %>%
  kable_styling(
    latex_options = c("scale_down")
  ) %>%
  kable_paper(full_width = F) %>%
  add_header_above(header) %>%
  collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
  save_kable(file_name)
```
